Who Stays Single? Exploring the Factors Behind Non-Marriage in the United States in 2023

### 2024-12-03 paper/paper.qmd
Final commit

Similarly, income plays a complementary but less pronounced role. @fig-income-distribution illustrates that unmarried individuals tend to cluster in lower income brackets, with the majority earning less than $40,000 annually. This highlights the persistent importance of financial stability in marital decisions, although its impact appears secondary to education.

>>>>

Similarly, income plays a complementary but less pronounced role. @fig-Income-Unmarried illustrates that unmarried individuals tend to cluster in lower income brackets, with the majority earning less than $40,000 annually. This highlights the persistent importance of financial stability in marital decisions, although its impact appears secondary to education.
